\documentclass[10pt,a4paper, typewriter]{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry} % Document margins
\name{Holly Kwan} % Your name
\address{Dallas, TX 75252 | hxk132830@utdallas.edu} % Your address and email
\address{ hollykwan.com | Github: hollykhk | Devpost: hollykhk}
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf The University of Texas at Dallas, Richardson, TX} \hfill {\em August 2013 - May 2018} \\ 
B.S. in Computer Science \\
{\bf The Bellaire High School, Bellaire, TX} \hfill {\em August 2009 - May 2013} \\ 
8 Advanced Placement Classes
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}
\begin{rSubsection}{CS Outreach - UT Dallas}{September 2017 - November 2017}{Instructor}{Richardson, TX}
\item Taught a class twenty of students computer science using MIT Scratch.
\item Advised students to use MIT Scratch at their leisure time. 
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{The Mercury - UT Dallas - Student Media}{September 2015 - October 2016}{Student Media Worker}{Richardson, TX}
\item Distributed hundred of newspapers to university and community to educate students on news on campus and managed a booth on campus to promote the Student Media to faculties, students, and staffs.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Height Family Aquatic Center - The City of Richardson}{May 2016 - August 2016}{Lifeguard}{Richardson, TX}
\item Supervised hundred of swimmers and managed the pool grounds at the City of Richardson.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS & AWARDS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS | AWARDS}
\begin{rSubsection}{Smart ID - University workshop}{September 2017 - November 2017}{1st place}{Richardson, TX}
\item Implemented an application to facilitate the business of card management for a digital identity system.
\item Received a winning honor solely by competing against a class of thirty students.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Foodie - TAMUhack}{October 2016}{Top 10 Hack and Best Use of Google API Prize}{College Station, TX}
\item Developed an Android Application to help customers to make better dietary and culinary choices utilize OCR technology, Duck Duck Go API, and George Knowledge Graph API with Python. 
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{CrashBoulder - HackCU III}{May 2016 - August 2016}{}{}
\item Built a web application of Colorado transportation recommendations using AngularJS and NodeJS.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{ACTIVITIES | CERTIFICATIONS}
\begin{rSubsection}{IEEE Software Testing - JUnit}{September 2017 - November 2017}{}{}
\item Implemented a series of test cases to evaluate the Java program and optimize branch coverage.
\end{rSubsection}
\begin{rSubsection}{User Experience Club - UT Dallas}{September 2017 - November 2017}{Treasurer}{Richardson, TX}
\item Managed the fiscal operation and allocated necessary expenses for educational activities.
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Strengths}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C++, Java, Verilog, HTML, CSS \\
Tools & Node, Angular, Git, Linux, Latex 
\end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
